Baseline centering problem

### 2018-12-10 paper/tangotd.tex

Another possibility is to learn a goal-oriented policy towards desired
\emph{features} of the final state $s'$. Given a basis $(\Psi_i)$ of
features, and a set of coefficient $\alpha_i$, one might want
$\pi_\theta(a|s,(\alpha_i))$ to produce a policy that maximizes the
expected reward $\sum \alpha_i \Psi_i$ (thus, simultaneously learning to
solve a number of RL problems). 
This can be done either via learning a value function $V(s,(\alpha_i))$
then actor-critic, or via an eligibility-trace-like thing, but

>>>>

Another possibility is to learn a goal-oriented policy towards desired
\emph{features} of the final state $s'$. Given a basis $(\Psi_i)$ of
features, and a set of coefficient $\alpha_i$, one might want
$\pi_\theta(a|s,(\alpha_i))$ to produce a policy that maximizes the
expected reward $\sum \alpha_i \Psi_i$ (thus, simultaneously learning to
solve a number of RL problems). 
This can be done either via learning a value function $V(s,(\alpha_i))$
then actor-critic, or via an eligibility-trace-like thing (but then it
has to be on-policy, for which policy??)
